---
title: "Pitch"
author: "Glenn Matias"
date: "August 9, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview
This project aims to predict the number of Households in a population of people using Regression.

The dataset used is the Philippines' National Statistics office's data on the country's information about its population. The dataset contains the following information:

- Region
- Barangay
- Province
- Population
- City



## R Code for generating Linear model

```{r echo = TRUE}
    populationData = read.csv(file="population.csv", head=TRUE)
    plot(populationData$Population, populationData$Nhouseholds, 
         xlab = "Population",ylab = "Number of Households in Region",
         bty = "n", pch = 16,xlim = c(0, 100000), ylim = c(0, 15000))
    #omitted lines meant for shiny
```

## Purpose of Project

In the Philippines, trying to account for population and other statistic measures (e.g. number of households, number of Barangays, etc.) can be costly and requires a lot of manpower and manhours. With this simple product, there is no need for manual door-to-door mode of counting households in order to get how many households are in a population. This will ultimately save manhours and manpower from being spent via door-to-door counting.

## Reference and links
- Github: https://github.com/GlennMatias/DevelopingDataProductsProject
- ShinyApp: https://glennmatias.shinyapps.io/DevelopingDataProductsProject/

